%   Filename    : chapter_2.tex 
\chapter{Review of Related Literature}
\label{sec:relatedlit}



\section{Mental Health Awareness}
Mental health awareness is the general plan to recognize and understand mental health problems to plan on their mitigation \shortcite{kolappa2013no,srivastava2016mental}. Recognizing and understanding problems to one’s mental health is to be knowledgeable enough of mental health \cite{jorm2000mental} which they can do with their peers and other nonprofessional external strategies \shortcite{rebello2014innovative}. On the other hand, preventing the effects of a mental health problem might take a whole nation to be successful. Involvement of conventional media, government programs, educational system, industry, the Internet, social media, and cellphones, and crowdsourcing might help diminish both the problem itself and its effects \shortcite{srivastava2016mental}. Therefore, making a website for guidance counselors and psychologically distressed students at the University of the Philippines Visayas-Miagao (UPV-M) would be a step closer to the goal of awareness and mitigation of mental health problems in the community. 

\section{Mental health of Students}
%The mental health of college students in the university greatly affects academic performance, and interpersonal and intrapersonal skills \cite{brackney1995psychopathology}. Students who experienced test anxiety, decline academic help, have low environment study maintenance, and difficulty persistence are significantly related to having high psychological distress \shortcite{brackney1995psychopathology}. 



According to \citeA{brackney1995psychopathology}, the mental health of college students in the university greatly affects academic performance, and interpersonal and intrapersonal skills. Students who experienced test anxiety, decline academic help, have low environment study maintenance, and difficulty persistence are significantly related to having high psychological distress. It was, also, determined that students’ information processing skills can also weaken, too \cite{kitzrow2003mental}. Students who have a negative interpersonal relationship with other people, may it be teachers, other students, and/or family members; and experienced loneliness within themselves, are both causes and effects of mental health problems \cite{american1980diagnostic}. Thus, having a website where UPV-M students can communicate with guidance counselors through direct messaging can lessen the damage and the degree of their mental health problem can cause and get. 

\section{Guidance Counseling in Universities}
The purpose of guidance and counseling service in school provide general education where it aims to assist students in fulfilling their basic physiological needs, understanding themselves and accepting others, developing associations with peers, balancing between permissiveness and controls in the educational setting, realizing successful achievement, and providing opportunities to gain independence \cite{heyden2011counseling}. Guidance and counseling services prepare students to assume increasing responsibility for their decisions and grow in their ability to understand and accept the results of their choices \shortcite{gibson2008introduction}. According to the \shortciteA{ea1982}, every student has the right to school guidance and counseling services, thus universities and schools must offer these services. In the UPV, the Guidance and Counseling offer services such as counseling, psychological testing, Career and Guidance, Graduate Placement and Follow-up, Human Development Services, and Peer Facilitating programs. 

\section{Online Counseling}
Due to COVID-19, online platforms are used daily by many. The use of online platforms in counseling shows no significant difference compared to face-to-face \cite{zeren2020effectiveness}. The University of the Philippines Visayas conducts its own online counseling and guidance services using social media platforms (e.g., Facebook) and through this, there are various modalities of communication that enable counselees to choose. However, the use of social media as a platform for school activity may harm the personal privacy of the students. Thus, creating a system for school guidance and counseling services may help in securing students’ data and privacy. 

\section{Appointment Booking}
Appointment booking is very important in medical offices and clinics or even in business transactions since these manage the flow of patients or clients. By doing it manually, there are possibilities that you can miss someone’s transactions when you are dealing with hundreds of clients or patients \shortcite{idowu2014dependable}. Patients line up outside the hospitals or institutions, waiting for their turn without any assurance of what time will they be assisted. This kind of situation always happens when appointments and schedules are not present or are not being utilized well. As the world also developing, shifting this kind of management flow in the hands of the internet, or even on LANs, having a good database for these appointments is beneficial for the company or clinic. Having a good management flow for the patients gives a huge benefit not just to the businesses or clinics, but for the patients themselves. The assurance of the correct schedule and appointments helps in gaining improvement in providing good healthcare for society. 

\section{Mailing Verification}
The use of protocols and systems is one of the methods used for e-mail verification \cite{abadi2002certified}. Protocols cover main security issues, but not all. These main security issues are secrecy, and receipt and proofs are mostly the responsibility of the verifier. Secrecy is when the verifier can automatically prove that the process preserved the secrecy of the sent message, and the receipt is the proof that the receiver did really receive the message which can be seen realistically \cite{abadi2005computer}. More so, e-mail verification using the system or trusted third party is together with the same protocols aforementioned above. The method proves by actuality: (1) Receiver must receive the message sent by the sender for the sender to have a receipt before the receiver can read the message, and (2) For sender to have a receipt that receiver read the sent message, the receiver must read first the sent message. Protocol, in this method, also protects confidentiality \cite{abadi2002certified}. This concludes that the use of protocols and systems for e-mail verification are both the same in logical concepts due to protocols. Accordingly, the use of the school’s domain e-mail, protected with Google Protocol RPC \cite{protocolrpc}, by students and guidance counselors when using the website system will ensure data security and account safety which will prevent malicious conduct from external applications. 

\section{Record keeping to healthcare}
Recordkeeping is a primary aspect in analyzing, improving, and providing quality healthcare to patients \shortcite{rigby1998integrated, pirkle2012medical}. In UK’s primary care, there are six models of storage and management of records, these are records in general practice, records based in community trusts, “virtual” integrated records, management by the third party, the patient held records, and formalized use of messaging \cite{rigby1998integrated}. In the Philippines, the EMR or electronic medical records is used to store, access, and process sensitive medical data of patients for the use of the attending physicians and other extended healthcare professionals \cite{ebardo2019barriers}. The EMR is a combination of records based in community trusts and “virtual” integrated records in the UK. This is because “general practitioners have real-time terminals to the system when using records based in community trusts”, but “other healthcare professionals can still access as long as they are in the same organizations which are more likely to happen in the “virtual” integrated record” \cite{rigby1998integrated}. Having to know these, the sole purpose of recordkeeping is storage, accessibility, and analysis of patient's data to be used for improvement and administration of the best healthcare possible by the collaboration of different healthcare professionals \cite{rigby1998integrated, ebardo2019barriers}. Hence, for guidance counselors of UPV-M to have a system where they can store and access, as well as summarize records will help to enhance their campaign in mental health awareness. 


\section{Reference Technologies}
The guidance and counseling system is inspired by these working apps and websites: 
\begin{itemize}
\item NowServing website \cite{nowserving2020}
	\begin{itemize}
	\item NowServing is a working website and app from the Philippines for finding specialized doctors near the user and can be used for an online appointment for general healthcare with the doctor. 
	\end{itemize}
\item Better Help \cite{betterhelp2021}
	\begin{itemize}
	\item BetterHelp is known to be the world's largest therapy platform. It is a website for addressing mental health and offers various therapists that can help patients. 
	\end{itemize}
\item Others
	\begin{itemize}
	\item Other apps may be included after working on the prototype.
	\end{itemize}
\end{itemize}











